---
title: "R Blog Posts"
output: html_document
---

Histogram with GGPlot
http://www.r-bloggers.com/how-to-make-a-histogram-with-ggplot2/
```{r}
chol <- read.table(url("http://assets.datacamp.com/blog_assets/chol.txt"), header = TRUE)
                       
```


```{r, echo=FALSE}
qplot(chol$AGE, geom='histogram')  # Histogram  
```

```{r}
ggplot(data=chol, aes(chol$AGE)) + geom_histogram()
```

```{r}
qplot(chol$AGE, geom='histogram', binwidth=0.5, main="Histogram for Age",
                xlab='Age', fill=I('blue'), col=I('red'), alpha=I(0.2),
                xlim=c(20,50))

mode(I('blue'))
```
                
Note the `I()` functions here. They turn functions into categoricals and help. 

```{r}
ggplot(data=chol, aes(chol$AGE) ) + geom_histogram(
                                    col="red", alpha=0.4,breaks=seq(20,50, by=2), 
                                    aes(y=..density..), fill='green') +
       geom_density(col=2) + 
    labs(title="Histogram for Age") +
    labs(x="Age", y="Count")
      
```
Note that in a previous iteration of this, I was also introduced to `scale_fill_gradient("Count", low = "green", high = "red")` which is good for gradients and is just an added layer as well.


```{r}
ggplot(data=chol, aes(chol$AGE)) + 
  geom_histogram(aes(y =..density..), 
                 breaks=seq(20, 50, by = 2), 
                 col="red", 
                 fill="green", 
                 alpha = .2) + 
  geom_density(col=2) + 
  labs(title="Histogram for Age") +
  labs(x="Age", y="Count")

```


..count.. or `..density..` gives 

?I
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

# Using Logistic Regression with R
http://www.r-bloggers.com/how-to-perform-a-logistic-regression-in-r/

## Cleaning the Data

```{r}
training = read.csv('Data/titanic_train.csv')
library(Amelia)
missmap(training, main="Missing Values")
```

```{r}
data <- subset(training,select=c(2,3,5,6,7,8,10,12))
```

```{r}
data$Age[is.na(data$Age)] <- mean(data$Age,na.rm=T)
missmap(data)
is.factor(data$sex)
is.factor(data$Embarked)
contrasts(data$Sex)

```
The `contrasts` function shows how the variables have been dummified. 

```{r}
contrasts(data$Embarked)
data[is.na(data$Embarked),] # So there are zero missing rows
# This behaves much as expected

```
?contrasts
So here we can see that that there is no reference variable. 

```{r}
sample_size = floor(0.75 * nrow(data))
train_indices = sample(seq_len(nrow(data)), size= sample_size)
train = data[train_indices, ]
test = data[-train_indices, ]
class(test)

model = glm(Survived ~., family=binomial(link='logit'), data=train)

summary(model)
```

It's important to understand all the different parts of the code here. We are having the commas at the end of the dataframes because we are interested in all the columns. 

The `glm` function is used to fit generalized linear models. We use the binomial family because it is a binary outcome.  TODO: Fine the interpretation of these models and glm basics


```{r}
data[24,1] # Gives us one item
data[24, 1:3]
data[24, ]
```

So the second comma is always necessary to select the columns.

```{r}
anova(model, test="Chisq")

```
The table of deviance here shows the difference between the null deviance and the devaince with the model. TODO: ANOVA tables

```{r}
library(pscl)
pR2(model)

fitted_results = predict(model, newdata=test, type='response')


```
?predict.glm obtains predictions and standard errors of predictions from glm models. TODO: Find the different `type` arguments. 

```{r}
library(ROCR)
p <- predict(model, newdata=subset(test,select=c(2,3,4,5,6,7,8)), type="response")
?predict
pr <- prediction(p, test$Survived)
prf <- performance(pr, measure = "tpr", x.measure = "fpr")
plot(prf)

auc <- performance(pr, measure = "auc")
auc <- auc@y.values[[1]] # This just extracts the correct slot
auc
```
AUC is area under the ROC curve. The ROC box is a 1 by 1 box and so we can just use that as our maximum.

?performance

p

